Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-07 providence/sections/workload.tex
more workload

\begin{figure}
\includegraphics[width=.5\textwidth]{optimal_costs.png}
\caption{For varying round cost $c_r$, the optimal average cost achievable by each audit, as a fraction of the Providence values.}
\label{fig:optimal_costs}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{optimal_costs_with_precinct.png}
\caption{The average cost of the audits we simulated using workload function \ref{eq:round_and_precinct_cost}.}
\label{fig:optimal_ps}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=.5\textwidth]{optimal_costs.png}
\caption{For varying round cost $c_r$, the optimal average cost achievable by each audit, as a fraction of the Providence values. (We show the value for varying $c_r$ since the value of $c_r$ may differ significantly from case to case.) Note that values lower than $10^3$ are probably unrealistic in US statewide contests; in Virginia, $c_r=10^3$ corresponds to only about $15$ minutes of persontime per county as the overhead per round.}
\label{fig:optimal_costs}
\end{figure}

@@

\begin{figure}
\includegraphics[width=.5\textwidth]{optima_with_precinct_cost.png}
\caption{The average cost of the audits we simulated using workload function \ref{eq:round_and_precinct_cost}.}
\label{fig:optimal_ps}
\end{figure}
